### 2020-04-02 draft.tex
questions and minor edits

A polynomial functor $P : \Set \to \Set$ is a sum of representables
$$P(X) := \sum_{b \in B} X^{E_b}$$
and therefore depends on a family of sets $E_b$ depending on $b\in B$. This data is known
in the computer science literature as a ``container'', but since such an indexed
family of sets can be represented by as a function
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"] \\
    B
  \end{tikzcd}
\]
we will refer to it as a \emph{bundle}. We think of a bundle as a categorified
Young diagram:

@@

$B$ is the set of rows and $E_b$ is the set of boxes in row $b$ (possibly empty,
for generalities sake). We can see the polynomial functor
\begin{equation}\label{eqn.poly}
P(X) := \sum_{b \in B} X^{E_b}
\end{equation}
as sending a set $X$ to the set of ways to label a row of the correponding Young
diagram with elements of $X$.

@@

Polynomial functors as in \eqref{eqn.poly} get their name from the case in which $B$ and $E$ are finite sets. Consider the function $\term{card}~E_{(-)} : B \to \Nb$, which takes the cardinality of each column $E_b$. Letting $B_n := (\term{card}E_{(-)})\inv(n)$, i.e.\ $B_n$ is the set of columns with $n$ elements,
we find that the for any set $X$, the cardinality
$$|P(X)| = \sum_{n \in \Nb} |B_n||X|^n$$
is a polynomial in the cardinality of $X$. Similarly,
$$|D(X)| = \sum_{n \in \Nb} |B_n|n^{|X|}$$
resembles a Dirichlet series in the cardinality of $X$. Accordingly, we call such
sums of contravariant representables \emph{Dirichlet functors}. Readers who prefer more traditional algebraic notation can see \cite{SpivakMyers}, which was the set-theoretic inspiration for the present paper.\dis{Agree?}

We will show in this paper that Dirichlet functors are, quite robustly, the
contravariant analogue of polynomial functors. In particular, the many equivalent ways to
say that a functor is polynomial have contravariant analogues.
\begin{thm}[cite]\label{thm:polynomial.set.characterization}
  Let $P : \Set \to \Set$ be a functor. Then the following are equivalent.
  \begin{enumerate}
  \item $P$ is polynomial.
  \item $P$ is the sum of covariant representables.
  \item There is a bundle $\pi : E \to B$ together with a natural isomorphism
    $$P(X) \cong \sum_{b \in B} X^{E_b}.$$
    Or, equivalently, a natural isomorphism of $P$ with the composite
    $$\Set \xto{E^{\ast}} \Set_{/E} \xto{\pi_!} \Set_{/B} \xto{B_\ast} \Set.$$
  \item $P$ is accessible and preserves connected limits.
  \end{enumerate}
\end{thm}

Analogously, we will prove the following theorem.
\begin{thm}\label{thm:dirichlet.set.characterization}
Let $D : \Set\op \to \Set$ be a contravariant functor. Then the following are
equivalent.
\begin{enumerate}
\item $D$ is Dirichlet.
\item $D$ is the sum of contravariant representables.
\item There is a bundle $\pi : E \to B$ together with a natural isomorphism
  $$D(X) \cong \sum_{b \in B} E_b^X.$$
  Or, equivalently, a natural isomorphism of $D$ with the composite
  $$\Set\op \xto{(B^{\ast})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
  \xto{B_{\ast}} \Set.$$
\item $D$ preserves connected limits.
\end{enumerate}
\end{thm}

Note that we no longer need to assume accessiblity. This is a general feature of
the theory of Dirichlet functors; it is a bit ``smaller'' and more maneageable
than that of polynomials. In particular, a Dirichlet functor is determined by
its action on the terminal morphism $!_0 : 0 \to \ast$ of the empty set. As a corollary, Dirichlet functors form a topos.

\begin{thm}\label{thm:dirichlet.set.equivalence}
The functor $\Set^{\down} \to \type{Fun}(\Set\op, \Set)$, given by sending $\pi : E
\to B$ to the induced Dirichlet functor $X \mapsto \sum_{b \in B} E_b^X$, is
fully faithful, and so gives an equivalence
$$\Set^{\down} \simeq \Dir$$
between bundles and Dirichlet functors, with inverse given by evalutation at
$!_0 : 0 \to \ast$.
\end{thm}

Now, object-wise, a Dirichlet functor and a polynomial functor are determined by
the same data --- a bundle $\pi : E \to B$ of sets. Accordingly, one would
expect a transformation
$$X^N \mapsto N^X$$
turning polynomial functors into Dirichlet functors, and vice versa. But the
natural transformations between each sort of functor induce different morphisms
between the bundles; natural tranformations between polynomial functors induce
contravariant bundle morphisms, while natural transformations between Dirichlet
functors induce covariant bundle morphisms. However, if we restrict to those
morphisms of bundles which are \emph{isovariant} on the fibers --- that is, the
pullback diagrams of the form
\[
  \begin{tikzcd}
E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] \arrow[dr, phantom,
"\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
B \arrow[r, "f"']                                       & B'                  
\end{tikzcd}
\]
which preserve the number of boxes in each row --- we find that such a morphism
is both a co- and contravariant morphism of bundles. It is well known that such
\emph{cartesian} morphisms of bundles correspond to \emph{cartesian} natural
transformations between polynomial functors (cite) --- those whose naturality
squares are pullbacks. This is true as well for Dirichlet functors.
\begin{thm}
A natural transformation $D \to D'$ of Dirichlet functors is Cartesian if and
only if the corresponding bundle map
\[
  \begin{tikzcd}[column sep=large]
E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] \arrow[dr, phantom,
"\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
B \arrow[r, "f"']                                       & B'                  
\end{tikzcd}
\]
is a pullback. As a corollary, we have an equivalence of categories
$$\type{Poly}_{\ulcorner} \simeq \Dir_{\ulcorner}$$
between polynomial functors with cartesian natural transfromations and Dirichlet
functors with cartesian natural transfromations.
\end{thm}

@@

Polynomial functors play another very important role: they are \emph{generating
  functors} for flat combinatorial species. That is, we have a (non-canonical)
identification
$$P(X) \cong \sum_{n \in \Nb} C_n \times X^n/n!$$
for sets $C_n$ on which the symmetric groups $\Aut(\underline{n})$ act freely
(for \emph{finitary} $P$, commuting with filtered colimits).
The generating functors for general combinatorial species --- the \emph{analytic
functors} --- are not in general polynomial due to a loss of information when
quotienting out by the action of the symmetric groups. This can be fixed by
instead taking \emph{homotopy quotients} of these actions.

@@

In \emph{$\infty$-Operads as Analytic Monads} \cite{GHK:Analytic.Monads},
Gepner, Haugseng, and Kock take this approach and develop the theory of
polynomial functors on homotopy types. In this setting, being analytic is a
property of \dis{some?} polynomial functors, and is equivalent to admitting a cartesian
map to the functor $\type{Sym}$ given by
$$\type{Sym}X := \sum_{n : \Nb} X^n \sslash n!$$

GHK prove $\infty$-categorical analogues of the above Theorem
\ref{thm:polynomial.set.characterization}.
\begin{thm}[\cite{GHK:Analytic.Monads}]\label{thm:polynomial.type.characterization}
Let $P : \Ha \to \Ha$ be a functor on the $\infty$-category of homotopy types.
Then the following are equivalent:
  \begin{enumerate}
  \item $P$ is polynomial.
  \item There is a bundle $\pi : E \to B$ of homotopy types together with a natural equivalence
    $$P(X) \simeq \sum_{b : B} X^{E_b}.$$
    Or, equivalently, a natural equivalence of $P$ with the composite
    $$\Ha \xto{E^{\ast}} \Ha_{/E} \xto{\pi_!} \Ha_{/B} \xto{B_\ast} \Ha.$$
  \item $P$ is accessible and preserves weakly contractible limits.
  \end{enumerate}
\end{thm}

Note that while this is a strong analogue, it is not a direct generalization:
not all connected limits are weakly contractible.

In Section \ref{sec:type.level}, we will prove analogues of Theorems
\ref{thm:dirichlet.set.characterization} and
\ref{thm:dirichlet.set.equivalence}. In particular, we will prove the following.

\begin{thm}\label{thm:dirichlet.type.characterization}
Let $D : \Set\op \to \Set$ be a contravariant functor. Then the following are
equivalent.
\begin{enumerate}
\item $D$ is Dirichlet.
\item There is a bundle $\pi : E \to B$ of homotopy types together with a natural equivalence
  $$D(X) \cong \sum_{b \in B} E_b^X.$$
  Or, equivalently, a natural equivalence of $D$ with the composite
  $$\Ha\op \xto{(B^{\ast})\op} (\Ha_{/B})\op \xto{[-, \pi]} \Ha_{/B}
  \xto{B_{\ast}} \Ha.$$
\item $D$ preserves weakly contractible limits.
\end{enumerate}
\end{thm}

In Section \ref{sec:ordinary.dirichlet.functors}, we will introduce the notion
of an \emph{ordinary} Dirichlet functor, a categorification of a Dirichlet
series
$$\sum_{n \in \Nb} a_n n^{-s}.$$
In the last installment of his blog \emph{This Week's Finds} (cite), Baez (joint with
Dolan) presents a functor of groupoids categorifying the Riemann Zeta function.
In later, unpublished work (cite), Baez and Dolan give an analogous
categorification of Hasse-Weil Zeta functions. We will recall some facts about
homotopy cardinality and construct these Zeda functors as ordinary Dirichlet
functors in our setting. We leave the investigation of Euler product formulas
and functional equations on the objective level to future work.

@@

Before diving in to the theory of Dirichlet functors, let's first consider the
category $\Set^{\down}$ of bundles of sets.

\begin{prop}
  There is an adjoint quintuple:
  \[
    \begin{tikzcd}
      \Set \arrow[r, "\const"] \arrow[r, leftarrow, shift left = 5,
      "\term{cod}"] \arrow[r, leftarrow, shift right = 5, "\term{dom}"]
      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10, "!_{(-)}"] & \Set^{\down}
    \end{tikzcd}
  \]
  All of the functors $\Set \to \Set^{\down}$ are fully faithful.
\end{prop}
\begin{proof}
There is an adjoint triple $\begin{tikzcd} \ast \arrow[r,leftarrow] \arrow[r,
  bend left] \arrow[r, bend right] & \down \end{tikzcd}$. The middle three
functors are given by restricting along this adjoint triple; the outer two are
given by Kan extending, or more concretely:
  $$X \mapsto \begin{tikzcd} 0 \arrow[d, "!^X"] \\ X \end{tikzcd}$$
  $$X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}$$
It is easy to see that the unit $X \to \term{dom} !_{X}$ is an isomorphism (it is in
fact an identity), so $!_{(-)}$ is fully faithful. Therefore, all the functors
going from $\Set \to \Set^{\down}$ are fully faithful.
\end{proof}

We prove a quick fact we will use later.
\begin{lem}\label{lem:bang.preserves.connected.colimits}
  The functor $!_{(-)}$ preserves connected colimits.
\end{lem}
\begin{proof}
  To see that $!_{(-)}$ preserves connected colimits, recall that colimits in $\Set^{\down}$ are calculated pointwise. It remains to show, then, that the map
  \[
    \begin{tikzcd}
    \colim S_i \arrow[r, equals] \arrow[d] & \colim S_i \arrow[d] \\
    \colim \ast \arrow[r] & \ast 
    \end{tikzcd}
  \]
  is an isomorphism in $\Set^{\down}$, for which it suffices to show that
  $\colim \ast$ is terminal. But the colimit of the terminal diagram is the set
  of connected components of its indexing diagram -- since we assumed the
  indexing diagram was connected, this contains a single element.
\end{proof}

Now we will define the \emph{extent} of a bundle, the Dirichlet functor it
corresponds to. This sends a bundle
$\pi : E \to B$ to the functor
$$X \mapsto \sum_{b \in B} E_b^X.$$
We will, however, give a more abstract definition of the extent, and then
calculate a number of presentations of it.

\begin{defn}
  The functor $!_0 : \down \to \Set\op$ picking out the terminal morphism
  $!_0 : 0 \to 1$ by precomposition an evaluation functor
  $$\Set^{\down} \xleftarrow{\ev_{!_0}} \Fun(\Set\op, \Set).$$
  This functor admits a right adjoint by right Kan extension; we define the
  \emph{Dirichlet extent} functor $\ext : \Set^{\down} \to \Fun(\Set\op,
  \Set)$ to be this right adjoint:
  $$\ext_{\pi} :\equiv \term{ran}_{!_0} \pi.$$
\end{defn}

@@

\begin{prop}\label{prop:set.characterizing.extent}
  Let $\pi : E \to B$ be a bundle. The following are equivalent:
  \begin{enumerate}
  \item The extent $\ext_{\pi} : \Set\op \to \Set$ of $\pi$.
  \item The functor
    $$S \mapsto \sum_{b \in B} E_b^S,$$
    or equivalently the composite
  $$\Set\op \xto{(B^{\ast})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
  \xto{B_{\ast}} \Set.$$
\item The restricted representable functor
  $\Set^{\down}(!_{(-)}, \pi)$.
\item The functor
  $$S \mapsto \lim(\Hom_{\Set}(!_0, S) \to \down \xto{\pi} \Set)$$
  where $\Hom_{\Set}(!_0, S)$ is the slice category of $!_0 : \down \to
  \Set$ over $S$.
\item The functor
  $$S \mapsto \lim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft}
  \xto{\pi} \Set)$$
  where $(-)^{\triangleleft}$ is the \emph{left cone} 2-functor, adjoining an initial object.
  \end{enumerate}
\end{prop}
\begin{proof}
We have presented these results in order of most understandable to most
computational; we will prove it a somewhat opposite order.

First, we note that 
$$S \mapsto \lim(\Hom_{\Set\op}(S, !_0) \to \down \xto{\pi} \Set)$$
is the standard right Kan extension formulat for $\ext_{\pi} \equiv
\term{ran}_{!_0} \pi$. Noting that $\Hom_{\Set}(!_0, S) = \Hom_{\Set\op}(S,
!_0)$, we see that (1) is equivalent to (4). Furthermore, noting that
$\Hom_{\Set}(!_0, S)$ simply adjoins an initial object to (the discrete
category) $S$, we see that (4) is equivalent to (5).

Now, we note that every set $S$ is the colimit of the diagram $S^{\triangleleft}
\xto{\ast^{\triangleleft}} \xto{!_0} \Set$, namely:
\[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBoBGAXVJADcBDAGwFcYkRyQBfU9TXfIRTkK1Ok1btOPPtjwEiAZlE0GLNog7deIDHMFEALCvHqp22QIUoATCbWTNAHScBjKBBwIZu-vKHIdjZiDhogxBa++taBpMQhEmEAGtxiMFAA5vBEoABmAE4QALZIAKw0OBBIxD4FxWUVVYjktYUliOUglUg2rfUdjUiKfe1kXU0AbCNIIuNIUzp17XZziAt5bUODa1yUXEA
\begin{tikzcd}
              &              & S                                               &              &               \\
1 \arrow[rru] & 1 \arrow[ru] & \cdots                                          & 1 \arrow[lu] & 1 \arrow[llu] \\
              &              & 0 \arrow[llu] \arrow[lu] \arrow[ru] \arrow[rru] &              &              
\end{tikzcd}
\]
Since, by Lemma \ref{lem:bang.preserves.connected.colimits}, $!_{(-)}$
preserves connected colimits, {\color{red} TODO}.

Finally, we note that the set $\Set^{\down}(!_X, \pi)$ is naturally
isomorphic to the set $\sum_{b \in B} E_b^X$.
\end{proof}

@@

Every set is the connected colimit of the diagram $S^{\triangleleft} \to
\down \xto{!_0} \Set$, and therefore if $D$ preserves this limit, then
$D(S)$ is precisely the above limit $\ext_{D!_0}(S)$.
\end{proof}

@@

\begin{cor}
  Let $D$ be a Dirichlet functor. Then the category
  $\Dir_{/_{\ulcorner} D}$
  of Dirichlet functors with a cartesian map to $D$ is a topos.
\end{cor}
\begin{proof}
By Theorem \ref{thm:set.poly.cart.equiv.dir.cart}, this category is equivalent
to $\type{Poly}_{/_{\ulcorner} P}$ for a polynomial $P$. But this is a topos as
observed in Remark 2.6.2 of \cite{GHK:Analytic.Monads}.
\end{proof}

\section{Dirichlet Functors on Homotopy Types} \label{sec:type.level}

>>>>

\section{Introduction}
A polynomial functor $P : \Set \to \Set$ is a sum of representables
\begin{equation}\label{eqn.poly}
P(X) := \sum_{b \in B} X^{E_b}
\end{equation}
and therefore depends on a family of sets $E_b$ depending on $b\in B$. This data is known
in the computer science literature as a ``container'', but since such an indexed
family of sets can be represented by as a function
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"] \\
    B
  \end{tikzcd}
\]
we will refer to it as a \emph{bundle}. We think of a bundle as a categorified
Young diagram:

@@

$B$ is the set of rows and $E_b$ is the set of boxes in row $b$ (possibly empty,
for generalities sake). We can see the polynomial functor \eqref{eqn.poly}
as sending a set $X$ to the set of ways to label a row of the correponding Young
diagram with elements of $X$.

@@

Polynomial functors as in \eqref{eqn.poly} get their name from the case in which $B$ and $E$ are finite sets. Consider the function $\term{card}~E_{(-)} : B \to \Nb$, which takes the cardinality of each column $E_b$. Letting $B_n := (\term{card}E_{(-)})\inv(n)$, i.e.\ $B_n$ is the set of columns with $n$ elements,
we find that the for any set $X$, the cardinality
$$|P(X)| = \sum_{n \in \Nb} |B_n||X|^n$$
is a polynomial in the cardinality of $X$. Similarly,
$$|D(X)| = \sum_{n \in \Nb} |B_n|n^{|X|}$$
resembles a Dirichlet series in the cardinality of $X$. Accordingly, we call such
sums of contravariant representables \emph{Dirichlet functors}. Readers who prefer more traditional algebraic notation can see \cite{SpivakMyers}, which was the set-theoretic inspiration for the present paper.\dis{Agree? Maybe there's a better place to put this?}

We will show in this paper that Dirichlet functors are, quite robustly, the
contravariant analogue of polynomial functors. In particular, the many equivalent ways to
say that a functor is polynomial have contravariant analogues.
\begin{thm}[cite]\label{thm:polynomial.set.characterization}
  Let $P : \Set \to \Set$ be a functor. Then the following are equivalent.
  \begin{enumerate}
  \item $P$ is polynomial.
  \item $P$ is the sum of covariant representables.
  \item There is a bundle $\pi : E \to B$ together with a natural isomorphism
    $$P(X) \cong \sum_{b \in B} X^{E_b}.$$
    Or, equivalently, a natural isomorphism of $P$ with the composite
    $$\Set \xto{\dis{\Delta_{!_E}}} \Set_{/E} \xto{\dis{\Pi_\pi}} \Set_{/B} \xto{\dis{\Sigma_{!_B}}} \Set.$$
  \item $P$ is accessible and preserves connected limits.
  \end{enumerate}
\end{thm}

Analogously, we will prove the following theorem.
\begin{thm}\label{thm:dirichlet.set.characterization}
Let $D : \Set\op \to \Set$ be a contravariant functor. Then the following are
equivalent.
\begin{enumerate}
\item $D$ is Dirichlet.
\item $D$ is the sum of contravariant representables.
\item There is a bundle $\pi : E \to B$ together with a natural isomorphism
  $$D(X) \cong \sum_{b \in B} E_b^X.$$
  Or, equivalently, a natural isomorphism of $D$ with the composite
  $$\Set\op \xto{(\Delta_{!_B})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
  \xto{\Sigma_{!_B}} \Set.$$
\item $D$ preserves connected limits.
\end{enumerate}
\end{thm}

Note that we no longer need to assume accessiblity. This is a general feature of
the theory of Dirichlet functors; it is a bit ``smaller'' and more manageable
than that of polynomials. In particular, a Dirichlet functor is determined by
its action on the terminal morphism $!_0 : 0 \to \ast$ of the empty set \dis{also the terminal twisted arrow; any relation to GHK?}. As a corollary, Dirichlet functors form a topos.

\begin{thm}\label{thm:dirichlet.set.equivalence}
The functor $\Set^{\down} \to \type{Fun}(\Set\op, \Set)$, given by sending $\pi : E
\to B$ to the induced Dirichlet functor $X \mapsto \sum_{b \in B} E_b^X$, is
fully faithful, and so gives an equivalence
$$\Set^{\down} \simeq \Dir$$
between the topos of bundles and the category of Dirichlet functors, with inverse given by evalutation at
$!_0 : 0 \to \ast$.
\end{thm}

Now, object-wise, a Dirichlet functor and a polynomial functor are determined by
the same data --- a bundle $\pi : E \to B$ of sets. Accordingly, one would
expect for any set $N$ a transformation
$$X^N \mapsto N^X$$
turning polynomial functors into Dirichlet functors, and vice versa. But the
natural transformations between each sort of functor induce different morphisms
between the bundles; natural transformations between polynomial functors induce
contravariant bundle morphisms, while natural transformations between Dirichlet
functors induce covariant bundle morphisms. However, if we restrict to those
morphisms of bundles which are \emph{isovariant} on the fibers --- that is, the
pullback diagrams of the form
\[
  \begin{tikzcd}[column sep=large]
E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] \arrow[dr, phantom,
"\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
B \arrow[r, "f"']                                       & B'                  
\end{tikzcd}
\]
which preserve the number of boxes in each row --- we find that such a morphism
is both a co- and contravariant morphism of bundles. It is well known that such
\emph{cartesian} morphisms of bundles correspond to \emph{cartesian} natural
transformations between polynomial functors (cite) --- those whose naturality
squares are pullbacks. This is true as well for Dirichlet functors.
\begin{thm}
A natural transformation $D \to D'$ of Dirichlet functors is Cartesian if and
only if the corresponding bundle map
\[
  \begin{tikzcd}[column sep=large]
E \arrow[r, "\term{tot}(f_{\sharp})"] \arrow[d, "\pi"'] \arrow[dr, phantom,
"\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
B \arrow[r, "f"']                                       & B'                  
\end{tikzcd}
\]
is a pullback. As a corollary, we have an equivalence of categories
$$\type{Poly}_{\ulcorner} \simeq \Dir_{\ulcorner}$$
between polynomial functors with cartesian natural transfromations and Dirichlet
functors with cartesian natural transfromations.
\end{thm}

@@

Polynomial functors play another very important role: they are \emph{generating
  functors} for flat combinatorial species. That is, we have a (non-canonical)
identification
$$P(X) \cong \sum_{n \in \Nb} C_n \times X^n/n!$$
for sets $C_n$ on which the symmetric groups $\Aut(\underline{n})$ act freely
(for \emph{finitary} functors $P$, i.e.\ those that commute with filtered colimits).
The generating functors for general combinatorial species --- the \emph{analytic
functors} --- are not in general polynomial due to a loss of information when
quotienting out by the action of the symmetric groups. This can be fixed by
instead taking \emph{homotopy quotients} of these actions.

@@

In \emph{$\infty$-Operads as Analytic Monads} \cite{GHK:Analytic.Monads},
Gepner, Haugseng, and Kock take this approach and develop the theory of
polynomial functors on homotopy types. In this setting, being analytic is a
property of \dis{some?} polynomial functors, and is equivalent to admitting a cartesian
map to the functor $\type{Sym}$ given by
$$\type{Sym}X := \sum_{n : \Nb} X^n \sslash n!$$
\dis{This is the homotopy quotient?}

Let $\Ha$ be the $\infty$-category of homotopy types. GHK prove $\infty$-categorical analogues of the above Theorem
\ref{thm:polynomial.set.characterization}.
\begin{thm}[\cite{GHK:Analytic.Monads}]\label{thm:polynomial.type.characterization}
For any functor $P : \Ha \to \Ha$, the following are equivalent:
  \begin{enumerate}
  \item $P$ is polynomial.
  \item There is a bundle $\pi : E \to B$ of homotopy types together with a natural equivalence
    $$P(X) \simeq \sum_{b : B} X^{E_b}.$$
    Or, equivalently, a natural equivalence of $P$ with the composite
    $$\Ha \xto{E^{\ast}} \Ha_{/E} \xto{\pi_!} \Ha_{/B} \xto{B_\ast} \Ha.$$
  \item $P$ is accessible and preserves weakly contractible limits.
  \end{enumerate}
\end{thm}

Note that while this is a strong analogue, it is not a direct generalization of \cref{thm:polynomial.set.characterization}:
though it is true that in 1-categories all connected limits are weakly contractible, this is not true in general.

In Section \ref{sec:type.level}, we will prove analogues of Theorems
\ref{thm:dirichlet.set.characterization} and
\ref{thm:dirichlet.set.equivalence}. \dis{What analogue of \ref{thm:dirichlet.set.equivalence} are we proving?} In particular, we will prove the following.

\begin{thm}\label{thm:dirichlet.type.characterization}
Let $D : \Set\op \to \Set$ \dis{Do you mean $\Ha$ here?} be a contravariant functor. Then the following are
equivalent.
\begin{enumerate}
\item $D$ is Dirichlet. \dis{In what sense?}
\item There is a bundle $\pi : E \to B$ of homotopy types together with a natural equivalence
  $$D(X) \cong \sum_{b \in B} E_b^X.$$
  Or, equivalently, a natural equivalence of $D$ with the composite
  $$\Ha\op \xto{(B^{\ast})\op} (\Ha_{/B})\op \xto{[-, \pi]} \Ha_{/B}
  \xto{B_{\ast}} \Ha.$$
\item $D$ preserves weakly contractible limits.
\end{enumerate}
\end{thm}

In Section \ref{sec:ordinary.dirichlet.functors}, we will introduce the notion
of an \emph{ordinary} Dirichlet functor, a categorification of a Dirichlet
series
$$\sum_{n \in \Nb} a_n n^{-s}.$$
In the last installment of his blog \emph{This Week's Finds} (cite), Baez (joint with
Dolan) presents a functor of groupoids categorifying the Riemann Zeta function.
In later, unpublished work (cite), Baez and Dolan give an analogous
categorification of Hasse-Weil Zeta functions. We will recall some facts about
homotopy cardinality and construct these Zeta functors as ordinary Dirichlet
functors in our setting. We leave the investigation of Euler product formulas
and functional equations on the objective level to future work.

@@

Before diving in to the theory of Dirichlet functors, let's first consider the
category $\Set^{\down}$ of bundles of sets and univariant bundle maps.

\begin{prop}
  There is an adjoint quintuple:
  \[
    \begin{tikzcd}
      \Set \arrow[r, "\const"] \arrow[r, leftarrow, shift left = 5,
      "\term{cod}"] \arrow[r, leftarrow, shift right = 5, "\term{dom}"]
      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10, "!_{(-)}"] & \Set^{\down}
    \end{tikzcd}
  \]
  All three functors $\Set \to \Set^{\down}$ are fully faithful.\dis{I had six; why leave one off?}
\end{prop}
\begin{proof}
There is an adjoint triple $\begin{tikzcd} \ast \arrow[r,leftarrow] \arrow[r,
  bend left] \arrow[r, bend right] & \down \end{tikzcd}$. The middle three
functors---$\term{cod}$, $\const$, and $\term{dom}$---are given by restricting along this adjoint triple; the outer two are
given by Kan extending, or more concretely:
  \begin{equation}\label{eqn.bangbang}
  X \mapsto \begin{tikzcd} 0 \arrow[d, "!^X"] \\ X \end{tikzcd}
  \qquad\text{and}\qquad
  X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}
  \end{equation}
\dis{Shouldn't the notation $!^X$ and $!_X$ be switched, so that $X$ is contravariant in $X\to \ast$ and covariant in $0\to X$? It also matches the side of the arrow that $X$ is on in \eqref{eqn.bangbang}.} It is easy to see that the unit $X \to \term{dom} !_{X}$ is an isomorphism (it is in
fact an identity), so $!_{(-)}$ is fully faithful. Therefore, all three functors
going from $\Set \to \Set^{\down}$ are fully faithful.
\end{proof}

We prove a quick fact we will use later.
\begin{lem}\label{lem:bang.preserves.connected.colimits}
  The functor $!_{(-)}\colon\Set\to\Set^{\down}$ from \eqref{eqn.bangbang} preserves connected colimits.
\end{lem}
\begin{proof}
  To see that $!_{(-)}$ preserves connected colimits, recall that colimits in $\Set^{\down}$ are calculated pointwise. It remains to show, then, that the map of bundles
  \[
    \begin{tikzcd}
    \colim S_i \arrow[r, equals] \arrow[d] & \colim S_i \arrow[d] \\
    \colim \ast \arrow[r] & \ast 
    \end{tikzcd}
  \]
  is an isomorphism in $\Set^{\down}$, for which it suffices to show that
  $\colim \ast$ is terminal. But the colimit of a diagram of terminal objects is the set
  of connected components of its indexing category. Since we assumed the
  indexing category was connected, this contains a single element.
\end{proof}

Now we will define the \emph{extent} of a bundle $\pi$ to be the Dirichlet functor $\ext_\pi: \Set\to\Set$ that it
corresponds to. This sends a bundle
$\pi : E \to B$ to the functor
$$X \mapsto \sum_{b \in B} E_b^X.$$
We will, however, give a more abstract definition of the extent, and then
calculate a number of presentations of it.

\begin{defn}\label{def.extent}
  Consider the functor $!_0 : \down \to \Set\op$ picking out the unique morphism $1\to 0$ in $\Set\op$. Sending a functor $\Set\op\to\Set$ to its precomposition with $!_0$ gives an evaluation functor
  $$\Set^{\down} \xleftarrow{\ev_{!_0}} \Fun(\Set\op, \Set).$$
  \dis{I worry about the size of $\Fun(\Set\op,\Set)$.}
  This functor admits a right adjoint by right Kan extension along $!_0$; we define the
  \emph{Dirichlet extent} functor $\ext : \Set^{\down} \to \Fun(\Set\op,
  \Set)$ to be this right adjoint. It sends any bundle $\pi$ to
  $$\ext_{\pi} :\equiv \term{ran}_{!_0} \pi.$$
\end{defn}

@@

\begin{prop}\label{prop:set.characterizing.extent}
  Let $\pi : E \to B$ be a bundle. The following are equivalent:
  \begin{enumerate}
  \item The extent $\ext_{\pi} : \Set\op \to \Set$ of $\pi$ from \cref{def.extent}.
\item \dis{Add this?} The pullback functor sending a set $S$ to 
\[
\begin{tikzcd}
	\ext_\pi(S)\ar[r]\ar[d]\arrow[dr, phantom,
      "\ulcorner" very near start]&
	B\ar[d]\\
	\Set(S,E)\ar[r]&
	\Set(S,B)
\end{tikzcd}
\]
  \item The functor
    $$S \mapsto \sum_{b \in B} E_b^S,$$
    or equivalently the composite
  $$\Set\op \xto{(B^{\ast})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
  \xto{B_{\ast}} \Set.$$
\item The restricted representable functor
  $\Set^{\down}(!_{(-)}, \pi)$.
\item The functor
  $$S \mapsto \lim(\Hom_{\Set}(!_0, S) \to \down \xto{\pi} \Set)$$
  where $\Hom_{\Set}(!_0, S)$ is the slice category of $!_0 : \down \to
  \Set$ over $S$.\dis{Is this Emily's notation for comma category?}
\item The functor
  $$S \mapsto \lim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft}
  \xto{\pi} \Set)$$
  where $(-)^{\triangleleft}$ is the \emph{left cone} 2-functor, adjoining an initial object.
  \end{enumerate}
\end{prop}
\begin{proof}
We have presented these results in order of most understandable to most
computational; we will prove it a somewhat opposite order.

First, we note that 
$$S \mapsto \lim(\Hom_{\Set\op}(S, !_0) \to \down \xto{\pi} \Set)$$
is the standard right Kan extension formula for $\ext_{\pi} \equiv
\term{ran}_{!_0} \pi$ as a conical limit. Noting that $\Hom_{\Set}(!_0, S) = \Hom_{\Set\op}(S,
!_0)$, we see that (1) is equivalent to (4). Furthermore, noting that
$\Hom_{\Set}(!_0, S)$ simply adjoins an initial object to (the discrete
category) $S$, we see that (4) is equivalent to (5).

Now, we note that every set $S$ is the colimit of the diagram $S^{\triangleleft}
\xto{\ast^{\triangleleft}}\down \xto{!_0} \Set$, namely:
\[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBoBGAXVJADcBDAGwFcYkRyQBfU9TXfIRTkK1Ok1btOPPtjwEiAZlE0GLNog7deIDHMFEALCvHqp22QIUoATCbWTNAHScBjKBBwIZu-vKHIdjZiDhogxBa++taBpMQhEmEAGtxiMFAA5vBEoABmAE4QALZIAKw0OBBIxD4FxWUVVYjktYUliOUglUg2rfUdjUiKfe1kXU0AbCNIIuNIUzp17XZziAt5bUODa1yUXEA
\begin{tikzcd}
              &              & S                                               &              &               \\
1 \arrow[rru] & 1 \arrow[ru] & \cdots                                          & 1 \arrow[lu] & 1 \arrow[llu] \\
              &              & 0 \arrow[llu] \arrow[lu] \arrow[ru] \arrow[rru] &              &              
\end{tikzcd}
\]
Since, by Lemma \ref{lem:bang.preserves.connected.colimits}, $!_{(-)}$
preserves connected colimits, {\color{red} TODO}.

Finally, we note that the set $\Set^{\down}(!_X, \pi)$ is naturally
isomorphic to the set $\sum_{b \in B} E_b^X$.\dis{add pullback?}
\end{proof}

@@

Every set $S$ is the connected colimit of the diagram $S^{\triangleleft} \to
\down \xto{!_0} \Set$, and therefore if $D$ preserves this limit, then
$D(S)$ is precisely the above limit $\ext_{D!_0}(S)$.
\end{proof}

@@

\begin{cor}
  Let $D$ be a Dirichlet functor. Then the category
  $\Dir_{/_{\ulcorner} D}$
  of Dirichlet functors with a cartesian map to $D$ is a topos.
\end{cor}
\begin{proof}
By Theorem \ref{thm:set.poly.cart.equiv.dir.cart}, this category is equivalent
to $\type{Poly}_{/_{\ulcorner} P}$ for a polynomial $P$. But this is a topos as
observed in Remark 2.6.2 of \cite{GHK:Analytic.Monads}.
\end{proof}
\dis{How does this topos compare to the topos $\Dir_{/D}$?}
\section{Dirichlet Functors on Homotopy Types} \label{sec:type.level}
